Optical characterization of gaps in directly bonded Si compound optics using infrared spectroscopy

### 2015-01-26 AO_bondedSi.tex
add circle-C from DTJ edits, required making new figures

\begin{equation}
	\ln{p(d,f,a,s|\lambda, T_{obs}, \sigma)} \propto \ln{p(d,f,a,s)} -0.5\;\boldsymbol{r^\intercal}\boldsymbol{C^{-1}}\boldsymbol{r} -0.5\;\ln{\det{\boldsymbol{C}}} \label{eqnPosterior}
\end{equation}

@@

\subsection{Spectra of direct bonded Si with known gap sizes}
\label{secKnownGaps}
Figures \ref{figVG03full} to \ref{figVG12} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.

>>>>

\begin{equation}
	\ln{p(d,f,a,s|\lambda, T_{obs}, \sigma)} \propto \ln{p(d,f,a,s)} -\frac{1}{2}\;\boldsymbol{r^\intercal}\boldsymbol{C^{-1}}\boldsymbol{r} -\frac{1}{2}\;\ln{\det{\boldsymbol{C}}} \label{eqnPosterior}
\end{equation}

@@

\subsection{Spectra of direct bonded Si with known gap sizes}
\label{secKnownGaps}

Figure \ref{figVG03full} shows a parameter determination for the measurement of a bond over a deep ($4000 \pm 200\;$nm) 100\% fill factor gap.  The analysis yields a best fit consistent with 100\% fill factor, and a depth of $3960 \pm 2\;$nm, well within the uncertainty of the physicsal measurement.  Figure \ref{figVG03part} shows a fit for a region of the same bonded pair where a nominally $4000\;$ nm deep, 2 mm wide trench crosses the field field scanned by the Cary 5000.  Analysis of this transmission curve gave a best fit depth of $4094 \pm 4\;$nm and a pattern fill factor of $4.6\% \pm 0.1\;\%$, both consistent with the part geometry.  These two results show that the formalism performs as expected on resonant gaps several wavelengths deep.

In our test samples, the nominal gap we have induced in the sample represents a lower limit to the actual gap since poor adhesion of the non-continuous patterns may result in gaps larger than intended.  In this case, we modify our mixture model \ref{eqnMix} to fix $f=0.5$ but allow two different depths:

\begin{equation}
	T_{mix} =  0.5 \times T_{e}(d_1) + 0.5 \times T_{e}(d_2) \label{eqnMix2Gaps}
\end{equation}

where the subscripts on $d$ distinguish the two depths.

Figure \ref{figVG12} shows the results for a bonded pair with a 50\% fill factor mesh where the grooves in the mesh had a measured depth of $49\pm6\;$nm.  The green band shows the predicted range for the transmission curve.  The measurements lie below this band.  Figure \ref{figVG12_corner} demonstrates that $d_1$ and $d_2$ are degenerate, but consistent with a $49 \pm 6\;$nm step function in the gap size distribution.

The presence of a number of bubbles both on and off the meshed areas of this and other samples (Figure \ref{figVS2021_IR_image}) lend credence to the idea that an additional gap of this magnitude was present at the position where we made the measurements but was not detected in the preparatory imaging.

\input{tbl_DerivedGapSizes}

Figures \ref{figVG03full} to \ref{figVG12} show examples of the predicted and measured IR spectra.  Figure \ref{figVG03_f100} shows an example spectrum in which the measurement is consistent with the prediction for a gap with the known conditions.  Meanwhile, Figure \ref{figVG12_f50} shows a spectrum in which the measurement marginally exceeds the prediction (by about $\sim 3 \sigma$).  Other parts show less consistency with the prediction due to the difficulty of direct-bonding Si in the absence of thermal annealing.
